Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-07-08 draftfinalreport_v4.Rnw
move generated tables to tables/ to indicate as such

# proportions of the naive population the would be covered if vaccinated by age groups now
propvCohort<-c(
round((sum(naive$Naive[3:6])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:12])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:17])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:19])/sum(naive$Naive)),2),
round((sum(naive$Naive[12:17])/sum(naive$Naive)),2),
round((sum(naive$Naive[12:19])/sum(naive$Naive)),2),
round((sum(naive$Naive[20:26])/sum(naive$Naive)),2),
round((sum(naive$Naive[20:36])/sum(naive$Naive)),2),
round((sum(naive$Naive[20:47])/sum(naive$Naive)),2),
round((sum(naive$Naive[1:30])/sum(naive$Naive)),2),
round((sum(naive$Naive[1:45])/sum(naive$Naive)),2),
round((sum(naive$Naive[8:100])/sum(naive$Naive)),2))
yr_range<-c("2-5","5-11","5-16","5-18","11-16","11-18","19-25","19-30","19-46","0-29","0-44",">8")
propvCohort<-cbind(yr_range,propvCohort)
propvCohort<-as.data.frame(propvCohort)
write.table(propvCohort,"vaccine_proportions_Cohort.txt",sep=",",row.names=T,col.names=F)
propsv = NULL
for (i in 1:20 ) {
  propsv[i] = round((sum(naive$Naive[i:13])/sum(naive$Naive)),2)
}
propsvAge = NULL
for (i in 1:20 ) {
  propsvAge[i]=paste(c(min(i:20)-1, max(i:20)-1),collapse="-")
}

@@

\begin{table}
\small
<<include=FALSE,echo=FALSE,results=tex>>=
dhb_vacc <- read.csv("dhb_vacc.csv")
print(xtable(dhb_vacc, digits=c(7,1,0,0,0,0,2)), include.rownames=F, floating=FALSE)
@
\caption{Epidemic size calculations. \textit{Population}: DHB Population, Statistics NZ 2013;  	
\textit{Na\"{\i}ve}: DHB na\"{\i}ve population $\left(x_0\times\text{Size}\right)$ (see \autoref{table:sero} for immunity estimates);
\textit{Outbreak}: Number infected in DHB in an outbreak of measles in the absence of any further vaccination assuming homogeneous mixing across DHB $\left(\Pe\right)$. Note outbreaks of these size lead to immunity rates that leave $\Rr_V$ below one until enough susceptibles are accumulated;	
\textit{Vaccination}:	Number of the currently na\"{\i}ve to be immunised in DHB to reduce $\Rr_V$ below one  $\left(\left(x_0-1/\Ro\right)\times\text{Size}\right)$; \textit{PC}: The proportion of the currently na\"{\i}ve population to vaccinate. These simulations assume homogeneous mixing. See \autoref{sub:mod_meth} for equations and further details on calculations.
}
\label{table:attack}
\end{table}

>>>>

# proportions of the naive population the would be covered if vaccinated by age groups now
propvCohort<-c(
round((sum(naive$Naive[3:6])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:12])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:17])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:19])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:26])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:36])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:47])/sum(naive$Naive)),2),
round((sum(naive$Naive[12:17])/sum(naive$Naive)),2),
round((sum(naive$Naive[12:19])/sum(naive$Naive)),2),
round((sum(naive$Naive[20:26])/sum(naive$Naive)),2),
round((sum(naive$Naive[20:36])/sum(naive$Naive)),2),
round((sum(naive$Naive[20:47])/sum(naive$Naive)),2),
round((sum(naive$Naive[1:30])/sum(naive$Naive)),2),
round((sum(naive$Naive[1:45])/sum(naive$Naive)),2),
round((sum(naive$Naive[8:100])/sum(naive$Naive)),2))
yr_range<-c("2-5","5-11","5-16","5-18","5-25","5-35","5-46","11-16","11-18","19-25","19-35","19-46","0-29","0-44",">8")
propvCohort<-cbind(yr_range,propvCohort)
propvCohort<-as.data.frame(propvCohort)
write.table(propvCohort,"vaccine_proportions_Cohort.txt",sep=",",row.names=T,col.names=F)
propsv = NULL
for (i in 1:20 ) {
  propsv[i] = round((sum(naive$Naive[i:13])/sum(naive$Naive)),2)
}
propsvAge = NULL
for (i in 1:20 ) {
  propsvAge[i]=paste(c(min(i:20)-1, max(i:20)-1),collapse="-")
}

@@

\begin{table}
\small
<<include=FALSE,echo=FALSE,results=tex>>=
dhb_vacc <- read.csv("tables/dhb_vacc.csv")
print(xtable(dhb_vacc, digits=c(7,1,0,0,0,0,2)), include.rownames=F, floating=FALSE)
@
\caption{Epidemic size calculations. \textit{Population}: DHB Population, Statistics NZ 2013;  	
\textit{Na\"{\i}ve}: DHB na\"{\i}ve population $\left(x_0\times\text{Size}\right)$ (see \autoref{table:sero} for immunity estimates);
\textit{Outbreak}: Number infected in DHB in an outbreak of measles in the absence of any further vaccination assuming homogeneous mixing across DHB $\left(\Pe\right)$. Note outbreaks of these size lead to immunity rates that leave $\Rr_V$ below one until enough susceptibles are accumulated;	
\textit{Vaccination}:	Number of the currently na\"{\i}ve to be immunised in DHB to reduce $\Rr_V$ below one  $\left(\left(x_0-1/\Ro\right)\times\text{Size}\right)$; \textit{PC}: The proportion of the currently na\"{\i}ve population to vaccinate. These simulations assume homogeneous mixing. See \autoref{sub:mod_meth} for equations and further details on calculations.
}
\label{table:attack}
\end{table}
